A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-09-25 paper1.tex
typos corrected

Modeling the formation and evolution of clusters with cosmological
hydrodynamical simulations has been progressively refined over the last years to
also include (subresolution models for) AGN feedback
\citep[e.g.,][]{2007MNRAS.380..877S, 2008MNRAS.387.1403S, 2008ApJ...687L..53P,
  2012MNRAS.420.2662D, 2012MNRAS.424..190G, 2013MNRAS.428.2366V}. While the
comparison to data and simulations with AGN feedback improved for integrated
thermal properties of large cluster samples
\citep{2012ApJ...758...74B,2012ApJ...758...75B}, there are still notable
differences for differential quantities such as the pressure profile
\citep{2013A&A...550A.131P} or the profile of gas mass fractions
\citep{2012arXiv1209.4082B}. These discrepancies (that have been more dramatic
in the past without AGN feedback) motivated the development of phenomenological
models of the ICM \citep[e.g.,][]{2005ApJ...634..964O,
  2012MNRAS.422..686C}. Here, we construct a simple and purely phenomenological
model that matches all available X-ray and Sunyaev-Zel'dovich (SZ) data with the
goal to facilitate comparison of future hydrodynamical simulations, to allow the
modeling of non-thermal cluster emission over the entire electromagnetic wave
band, and finally to enable the construction of cluster mock catalogs of the
(non-)thermal cluster emission of current and future surveys. Such a model for
the ICM needs to be complementd by a sample of cluster halos, which can either
be obtained by means of analytical expressions for the cluster mass function
(e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster simulations. In
this work, we make use of the recent collisionless $N$-body simulation {\em
  MultiDark}, which employs a $\Lambda$ cold dark matter cosmology
(\citealp{2011arXiv1104.5130P}; www.multidark.org).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SZ scaling relations}
\label{sec:5}
In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
\emph{Planck} COSMO sample with Malmquist bias correction,
which has a median redshift of $0.18$. Hence, we compare the data to our relation 
at the MultiDark snapshot $z=0.2$}. Our model reproduces the data remarkably well, except 
for the high-mass end where our simulations have a weaker constraining power due to the 
smaller box size in comparison to the survey volume of {\em Planck}. We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

@@

Summarizing, our SZ scaling relations compare very well to the result from
the \emph{Planck} collaboration. However, the comparison with the SPT and 
ACT samples is not as straightforward due to the different selection function 
of these telescopes with respect to \emph{Planck}, which results in a much
more (redshift) non-homogenous sample. Nevertheless, our mock clusters 
can reproduce well the median SPT and ACT populations. A more detailed
comparison would need the generation of light-cone mock catalogs,
including instrumental effects, which is beyond the scope of this 
work.}

>>>>

Modeling the formation and evolution of clusters with cosmological
hydrodynamical simulations has been progressively refined over the last years to
also include (sub-resolution models for) AGN feedback
\citep[e.g.,][]{2007MNRAS.380..877S, 2008MNRAS.387.1403S, 2008ApJ...687L..53P,
  2012MNRAS.420.2662D, 2012MNRAS.424..190G, 2013MNRAS.428.2366V}. While the
comparison to data and simulations with AGN feedback improved for integrated
thermal properties of large cluster samples
\citep{2012ApJ...758...74B,2012ApJ...758...75B}, there are still notable
differences for differential quantities such as the pressure profile
\citep{2013A&A...550A.131P} or the profile of gas mass fractions
\citep{2012arXiv1209.4082B}. These discrepancies (that have been more dramatic
in the past without AGN feedback) motivated the development of phenomenological
models of the ICM \citep[e.g.,][]{2005ApJ...634..964O,
  2012MNRAS.422..686C}. Here, we construct a simple and purely phenomenological
model that matches all available X-ray and Sunyaev-Zel'dovich (SZ) data with the
goal to facilitate comparison of future hydrodynamical simulations, to allow the
modeling of non-thermal cluster emission over the entire electromagnetic wave
band, and finally to enable the construction of cluster mock catalogs of the
(non-)thermal cluster emission of current and future surveys. Such a model for
the ICM needs to be complemented by a sample of cluster halos, which can either
be obtained by means of analytical expressions for the cluster mass function
(e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster simulations. In
this work, we make use of the recent collisionless $N$-body simulation {\em
  MultiDark}, which employs a $\Lambda$ cold dark matter cosmology
(\citealp{2011arXiv1104.5130P}; www.multidark.org).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SZ scaling relations}
\label{sec:5}
In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2012ApJ...758...74B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the 
\emph{Planck} COSMO sample with Malmquist bias correction,
which has a median redshift of $0.18$. Hence, we compare the data to our relation 
at the MultiDark snapshot $z=0.2$}. Our model reproduces the data remarkably well, except 
for the high-mass end where our simulations have a weaker constraining power due to the 
smaller box size in comparison to the survey volume of {\em Planck}. We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

@@

Summarizing, our SZ scaling relations compare very well to the result from
the \emph{Planck} collaboration. However, the comparison with the SPT and 
ACT samples is not as straightforward due to the different selection function 
of these telescopes with respect to \emph{Planck}, which results in a much
more (redshift) non-homogeneous sample. Nevertheless, our mock clusters 
can reproduce well the median SPT and ACT populations. A more detailed
comparison would need the generation of light-cone mock catalogs,
including instrumental effects, which is beyond the scope of this 
work.}
